Altering Backward Pass Gradients to improve Convergence

### 2022-11-14 paper.tex
Mod10
Mod11
Title change

\title{Altering Backward Pass Gradients improves Convergence}

@@

\begin{abstract}
In standard neural network training, the gradients in the backward pass are determined
by the forward pass. As a result, the two stages are coupled. This is how most neural
networks are trained currently. However, gradient modification in the backward pass has
seldom been studied in the literature. In this paper we explore decoupled training,
where we alter the gradients in the backward pass. We propose a simple yet powerful
method called PowerGrad Transform, that alters the gradients before the weight update in
the backward pass and significantly enhances the predictive performance of the neural
network. PowerGrad Transform trains the network to arrive at a better optima at
convergence. It is computationally extremely efficient, virtually adding no additional
cost to either memory or compute, but results in improved final accuracies on both the
training and test sets. PowerGrad Transform is easy to integrate into existing training
routines, requiring just a few lines of code. PowerGrad Transform makes it possible for
the network to better fit the training data. With decoupled training, PowerGrad
Transform improves baseline accuracies for ResNet-50 by 0.73\%, for SE-ResNet-50 by
0.66\% and by more than 1.0\% for the non-normalized ResNet-18 network on the ImageNet
classification task.
\end{abstract}

>>>>

\title{Altering Backward Pass Gradients to improve Convergence}

@@

\begin{abstract}
In standard neural network training, the gradients in the backward pass are determined
by the forward pass. As a result, the two stages are coupled. This is how most neural
networks are trained currently. However, gradient modification in the backward pass has
seldom been studied in the literature. In this paper we explore decoupled training,
where we alter the gradients in the backward pass. We propose a simple yet powerful
method called PowerGrad Transform, that alters the gradients before the weight update in
the backward pass and significantly enhances the predictive performance of the neural
network. PowerGrad Transform trains the network to arrive at a better optima at
convergence. It is computationally extremely efficient, virtually adding no additional
cost to either memory or compute, but results in improved final accuracies on both the
training and test sets. PowerGrad Transform is easy to integrate into existing training
routines, requiring just a few lines of code. PowerGrad Transform accelerates training
and makes it possible for the network to better fit the training data. With decoupled
training, PowerGrad Transform improves baseline accuracies for ResNet-50 by 0.73\%, for
SE-ResNet-50 by 0.66\% and by more than 1.0\% for the non-normalized ResNet-18 network
on the ImageNet classification task.
\end{abstract}
